Local to Global Mariculture Modelling

### 2025-07-28 index.qmd
Move feed details to index.qmd

>>>>

```{r}
#| label: feed-details

feed_params <- find_read(output_species_data_path, "feed_params")

feed_summary <- map_dfr(names(feed_params), function(feed) {
  df <- feed_params[[feed]]
  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
    contrib <- df[[macro]]$proportion * df[[macro]]$macro
    total <- sum(contrib)
    digest <- sum(df[[macro]]$digest * contrib) / total
        tibble(
      feed = feed,
      macro = macro,
      total = total,
      digest = digest
    )
  })
}) %>%
  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
         feed = factor(feed, levels = c("reference", "past", "future")),
         total_r = total * 100 %>% round(1),
         digest_r = digest * 100 %>% round(1))
```

| Feed | Protein (%, %) | Lipid (%, %) | Carbohydrate (%, %) |
|------|:----------:|:----------:|:----------:|
| Plant-dominant | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$digest, 1)`) | 
                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$digest, 1)`) | 
                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$digest, 1)`) |
| Marine-dominant | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$digest, 1)`) | 
                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$digest, 1)`) | 
                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$digest, 1)`) |
| Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`) | 
                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`) | 
                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`) |
